---
title: "Visualising molecular phenotypes inferred from individual samples using singscore, vissE and msigdb"
author:
  - name: Dharmesh D Bhuva
    affiliation:
      - Bioinformatics Division, Walter and Eliza Hall Institute of Medical Research, Parkville, VIC 3052, Australia
      - Department of Medical Biology, University of Melbourne, Parkville, VIC 3010, Australia
    email: bhuva.d@wehi.edu.au
  - name: Chin Wee Tan
    affiliation:
      - Bioinformatics Division, Walter and Eliza Hall Institute of Medical Research, Parkville, VIC 3052, Australia
      - Department of Medical Biology, University of Melbourne, Parkville, VIC 3010, Australia
    email: cwtan@wehi.edu.au
  - name: Melissa J Davis
    affiliation:
      - Bioinformatics Division, Walter and Eliza Hall Institute of Medical Research, Parkville, VIC 3052, Australia
      - Department of Medical Biology, University of Melbourne, Parkville, VIC 3010, Australia
      - Department of Biochemistry and Molecular Biology, Faculty of Medicine, Dentistry and Health Sciences, University of Melbourne, Parkville, VIC, 3010, Australia
    email: davis.m@wehi.edu.au
date: "`r format(Sys.time(), '%b %Y')`"
output:
  BiocStyle::html_document:
    toc_float: true
    fig_caption: true
    number_sections: true
nocite: | 
  @R-ggplot2, @R-knitr, @R-BiocWorkflowTools, @R-rmarkdown, @R-prettydoc
bibliography: [bibliography.bib, packages.bib]
vignette: >
  %\VignetteIndexEntry{Visualising molecular phenotypes inferred from individual samples using singscore, vissE and msigdb.}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
keywords: single sample, gene set scoring, signature scoring, visualisation
abstract: >
  Abstract
---

<p>

**R version**: `r R.version.string` <br /> **Bioconductor version**: `r BiocManager::version()` <br /> **Package version**: `r packageVersion("GenesetAnalysisWorkflow")`

</p>

```{r setup, include=FALSE}
#set knitr chunk options
knitr::opts_chunk$set(warning = FALSE, message = FALSE)

#load packages to avoid startup messages later in the code
suppressPackageStartupMessages({library(GenesetAnalysisWorkflow)})
library(ggplot2)
library(SummarizedExperiment)
library(edgeR)
library(GSEABase)
library(singscore)
library(msigdb)
library(vissE)

#automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'knitr', 'rmarkdown', 'prettydoc'
), 'packages.bib')
```

# Introduction

# Description of the biological problem

# Molecular phenotyping of individual samples

# Identifying and visualising higher-order phenotypes

# Summary

# Packages used {.unnumbered}

This workflow depends on various packages from version `r BiocManager::version()` of the Bioconductor project, running on `r version$version.string` or higher. The complete list of the packages used for this workflow are shown below:

```{r session_info}
sessionInfo()
```

# Acknowledgments {.unnumbered}

# References {.unnumbered}
